Push-Based Signal-Function Functional Reactive Programming (Thesis Proposal)

### 2012-05-12 Docs/Proposal/background.tex
Sentence structure correction for proposal background

There are two general approaches to FRP are ``classic'' FRP, where behaviors and signals are first-class and reactive objects, and ``signal-function'' FRP,
where transformers of signals and events are first-class and reactive objects.

>>>>

The two general approaches to FRP are ``classic'' FRP, where behaviors and signals are first-class and reactive objects, and ``signal-function'' FRP,
where transformers of signals and events are first-class and reactive objects.
